\documentclass[12pt]{article}
\title{Studygroup Reflection}
\author{Christoph Pickl}
%\date{\today}
\date{July 22, 2021}

\begin{document}
 \maketitle


 \section{Who (and how) am I?}

 \subsection{How do I see myself? What makes me me/unique?}

 This is difficult already, as I am not quite sure whether I repeat what other told me who I am, or wether I am going into old stories \ldots
 Simply put: I think I am a curious, adventurous little creature with lots of passion.

 To reduce everything to its inner workings, disect, understand and put it back together (divide and conquer).
 I can be considered as a walking paradoxon.

 \subsection{What are my core qualities?}

 My core quality is definitely \textbf{depth}. I bring structure and order. I like to abstract and to analyze to the fullest.
 I can see patterns where others usually can't see them.

 \subsection{What are my biggest challenges/fears?}

 Going too fast, so I lose the others or burn myself. Social conflicts due to different goals and expectations.


 \section{Why do I study psychology?}

 \subsection{What does psychology mean to me?}

 Love. Passion. Satisfaction. Understanding. Comfort. Peace.

 \subsection{What are my core motivations to study?}

 I felt this need, once I've tasted it, to have a proper foundation in this area.
 Also to heal, to understand, thus ultimately being able to have more peace and harmony with myself and other fellow humans.
 I realized, all my \textit{crazy thoughts} I had as a child, they pop up here again. I feel finally understood, home.

 \subsection{Where do I see myself in the future (job wise)?}

 Possible integrate part of my learnings into my corporate environment. Working mroe as a people manager.


 \section{Why do I want to join a studygroup?}

 \subsection{What are my wishes and expectations?}

 Motivate each other, meet on a regular base, creating a playground to learn.
 And share some tips and tricks to support with the daily student's life effort.

 \subsection{What are my fears and worst nightmares?}

 Wasting time. Unfocused meetings. Lack of passion and interest. Demotivation. Passiveness. Inequality in contribution.

 \subsection{How much and how (qualities) do I want to invest and contribute?}

 I want to go full throttle, haha. Realistically, I plan to invest 1-2 hours a day into the study.
 Part of it will definitely be for the studygroup.
 Using my primary qualities to provide a framework (structure) so we can fill in the content together.
 I definitely can and would like to contribute my IT expertise.

\end{document}
